---
title: "3_Make_figures_tables"
author: "Jaeseok Hwang"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---


## Knitr option

```{r, cache = F, echo = F, results = "hide"}
#####

library(knitr)

knitr::opts_chunk$set(
  cache = FALSE,
  echo = FALSE,
  warning = FALSE,
  cache.lazy = FALSE,
  fig.retina = 6,
  fig.height = 9,
  fig.width = 9,
  message = FALSE,
  error = TRUE
)

options(knitr.duplicate.label = "allow")

```


#### Packages 

```{r pacakages, cache = FALSE, results = "hide"}

library(here)
library(rmarkdown) # for rmarkdown options
library(bookdown) # for bookdown options
library(knitr) # for knitr options

library(sf) # for spatial data

library(data.table) # for data manipulation
library(tidyverse) # for data manipulation
library(dplyr) # for data manipulation
library(lubridate) # for date manipulation

library(tmap) # for mapping
library(ggplot2) # for plotting
library(kableExtra) # for table formatting
library(webshot) # for converting HTML to PNG
library(patchwork)
library(flextable)

```

### Read sources and load processed and analysis data

```{r source, echo = F, results = "hide"}

# Read functions for data processing 
source(here("Code","Main","0_Set_up_preparation.R"))
source(here("Code","Functions","functions_for_table_figure.R"))

# 101 field data
info_tb_list <-readRDS(here("Data", "Processed", "Analysis_results", "info_tb_list.rds"))

# Convert the list to a single data.table and remove the input_type and unit columns

info_tb_101 <- bind_rows(info_tb_list) %>%
                dplyr::select(-input_type, -unit)


```

###### CONTENTS ######

### Tables ###

# table1  - Data summary by year (2016 to 2023) 
# [summary_flex_tab1] / [table1_dat_summary.png]

# table2  - Analysis results table By the response type and seeding status (SQSR-EOSR) 
# [results_flex_tab2] / [table2_results_summary.png]

# table3 - Discussion Table 
# [on-going]
# [What happens to the farmer's expected scenario in terms of profit, and how the problem going in the bad weather cases]

### Figures ###

# figure1  - Net revenue after seed cost figure (1996 to 2023)
# [rev_seed_comb] / [fig1_rev_after_seed.png]

# figure2 - trial_design sampple figure  
# [td_figure] / [fig2_trial_design_sample.png]

# figure3 - EOSR ~ Precipitation and GDD ( In-season & 30 year Avg)
# [on-going]

# figure4 - Estimated Profit and Yield response by type (A2,B2,C)
# [on-going]

# figure5 - Dicussion Figure 
# [on-going]

################################
######### Tables ###############
################################


## Table1 Data summary by year (2016 to 2023)
# [summary_flex_tab1] / [table1_dat_summary.png]

```{r tables data table1, cache = T, results = "hide"}

# Table 1 data summary table 

info_tb_bind <- list()

# Loop through each year from 2016 to 2023
for (i in 1:8 ) {
  # Filter info_tb_102 for the current year
  info_tb_year <- info_tb_101[year == i+2015] 
  
  # Generate the file paths based on ffy for the current year
  all_ready_file_paths <- paste0(here("Data", "processed", "Analysis_ready"), "/", info_tb_year$ffy_id, "_merged_data.rds")
  
  # Read the RDS files for the current year
  comb_sf_list <- lapply(all_ready_file_paths, readRDS)

  mean_y_comb <- lapply(comb_sf_list, function(x) {
  mean(st_drop_geometry(x)$yield, na.rm = TRUE)
})
 
  info_tb_year$avg_yield <-  data.frame(mean_yield = unlist(mean_y_comb))

  info_tb_bind[[i]] <- info_tb_year

}

# data table that contains all the farm and experimental info by year 
info_tb_binded  <- bind_rows(info_tb_bind)

# Calculate mean, sd (with NA removal for usdsr), and field count by year
summary_table1 <- info_tb_binded[, .(
  field_count = .N , # Count the number of rows for each year
  avg_yield = sprintf("%.1f\n(%.1f)", round(mean(avg_yield), 1), round(sd(avg_yield), 1)),
  sqsr = sprintf("%.1f\n(%.1f)", round(mean(sqsr), 1), round(sd(sqsr), 1)),
  usdsr = sprintf("%.1f\n(%.1f)", round(mean(usdsr, na.rm = TRUE), 1), round(sd(usdsr, na.rm = TRUE), 1)),
  prcp_t = sprintf("%.1f\n(%.1f)", round(mean(prcp_t), 1), round(sd(prcp_t), 1)),
  gdd_t = sprintf("%.1f\n(%.1f)", round(mean(gdd_t), 1), round(sd(gdd_t), 1)),
  prcp_30 = sprintf("%.1f\n(%.1f)", round(mean(prcp_30), 1), round(sd(prcp_30), 1)),
  gdd_30 = sprintf("%.1f\n(%.1f)", round(mean(gdd_30), 1), round(sd(gdd_30), 1))
), by = year]

# Convert to a flextable for a formatted summary
summary_flex_tab1 <- flextable(summary_table1) %>%
  set_header_labels(
    field_count = "Field\nCount",
    year = "Year", 
    avg_yield = "Mean\nYield\n(bu/ac)",
    sqsr = "SQSR",
    usdsr = "USDA\nSR", 
    prcp_t = "Precipitation\n(In-Season)",
    gdd_t = "GDD\n(In-Season)",
    prcp_30 = "Precipitation\n(30Year)",
    gdd_30 = "GDD\n(30Year)"
  ) %>%
  align(align = "center", part = "all") %>%  # Center-align headers and body content
  autofit() %>%
  set_table_properties(layout = "autofit")

# Print the flextable  (TABLE1)
summary_flex_tab1

# Save the flextable as an HTML file
save_as_html(summary_flex_tab1, path = here("Results","Tables","table1_dat_summary.html"))

# Convert the HTML to a PNG image
webshot(here("Results","Tables","table1_dat_summary.html"), 
        file = here("Results","Tables","table1_dat_summary.png"),
        zoom = 2)  # Adjust zoom if you need higher resoluti

```


## Table2 ( Results table By Response type and estimated profit ) 
# [results_flex_tab2] / [table2_results_summary.png]

```{r tables result table2 by response type a to d , cache = T, results = "hide"}

# Step 1: Rename columns first
info_tb_binded <- info_tb_binded[, `:=`(
  eosr = esor,
  eosr_y = esor_y,
  eosr_p = esor_p
)]

# Step 2: Calculate the new different of seeding rate
# yield and profit by SQSR - EOSR 

info_tb_binded <- info_tb_binded[, `:=`(
  dif_s = sqsr - eosr,
  dif_y = sqsr_y - eosr_y,
  dif_p = sqsr_p - eosr_p
)]

# Step 3: Calculate the quadratic fit and yield maximizing seeding rate
# for each field
for(i in 1:length(info_tb_binded$ffy_id)){

  eval_s <-readRDS(here("Data", "processed", "Analysis_results",paste0(info_tb_binded$ffy_id[i],"_eval_tb.rds")))

    # Apply quadratic fit to each element in eval_s using map
    quad_fit = lm(yield_hat ~ s_rate + I(s_rate^2), data = eval_s)
    
    # Check the coefficients of the quadratic fit
    coef_2nd <- quad_fit$coef[3] 

    # Find the yield maximizing seeding rate
    yield_max_sr = eval_s[which.max(yield_hat), s_rate]
    
    info_tb_binded <- info_tb_binded[i, `:=`(
      quad_fit = coef_2nd,
      ymsr =  yield_max_sr
      )] 

}
# Step 4: Generate response type variable based on the conditions

info_tb_binded <-info_tb_binded[, resp_type := fcase(
  dif_s < 0 & quad_fit < 0 & ymsr == eosr, "A1",  # under_seed & corner sol
  dif_s < 0 & quad_fit < 0 & ymsr != eosr, "A2",
  dif_s > 0 & quad_fit < 0 & ymsr == eosr, "B1",  # over_seed & corner sol
  dif_s > 0 & quad_fit < 0 & ymsr != eosr, "B2",  # over_seed & corner sol
  quad_fit > 0, "C",
  default = NA_character_  # Default value if no conditions match
)]

info_tb_binded <- info_tb_binded[!is.na(resp_type)]
info_tb_binded[, resp_type := factor(resp_type, levels = c("A1", "A2", "B1", "B2", "C"))]

# Make results table by response type

result_table2 <- info_tb_tab2[, .(
  field_count = .N,  # Count the number of rows for each resp_type
  dif_s = sprintf("%.1f\n(%.1f)", round(mean(dif_s), 1), round(sd(dif_s), 1)),
  dif_y = sprintf("%.1f\n(%.1f)", round(mean(dif_y), 1), round(sd(dif_y), 1)),
  dif_p = sprintf("%.1f\n(%.1f)", round(mean(dif_p), 1), round(sd(dif_p), 1)),
  prcp_t = sprintf("%.1f\n(%.1f)", round(mean(prcp_t), 1), round(sd(prcp_t), 1)),
  gdd_t = sprintf("%.1f\n(%.1f)", round(mean(gdd_t), 1), round(sd(gdd_t), 1)),
  prcp_30 = sprintf("%.1f\n(%.1f)", round(mean(prcp_30), 1), round(sd(prcp_30), 1)),
  gdd_30 = sprintf("%.1f\n(%.1f)", round(mean(gdd_30), 1), round(sd(gdd_30), 1))
), by = resp_type]

setorder(result_table2, resp_type)

# Convert to a flextable for a formatted summary
result_flex_tab2 <- flextable(result_table2) %>%
  set_header_labels(
    field_count = "Field\nCount",
    dif_s = "Differences in \n Seeding Rate\n(K/ac)",
    dif_y = "Differences in \n Estimated Yield \n (bu/ac)",
    dif_p = "Differences in \n Estimated Profit \n ($/ac)",
    prcp_t = "Precipitation\n(In-Season)",
    gdd_t = "GDD\n(In-Season)",
    prcp_30 = "Precipitation\n(30 Year)",
    gdd_30 = "GDD\n(30 Year)"
  ) %>%
  align(align = "center", part = "all") %>%  # Center-align headers and body content
  autofit() %>%
  set_table_properties(layout = "autofit")

# Print the flextable 
result_flex_tab2

# Save the flextable as an HTML file
save_as_html(result_flex_tab2, path = here("Results","Tables","table2_results_summary.html"))

# Convert the HTML to a PNG image
webshot(here("Results","Tables","table2_results_summary.html"), 
        file = here("Results","Tables","table2_results_summary.png"),
        zoom = 2)  # Adjust zoom if you need higher resoluti


```



##################################
############ Figures #############
##################################

## Figure 1 ( Net revenue after seed cost figure 1996 to 2023)
# [rev_seed_comb] / [fig1_rev_after_seed.png]

```{r figure1 net revenue after seed cost, cache = T, results = "hide"}

corn_ers <-read.csv(here("Data","Raw","corn_cost_return.csv"),header = T)
ppi_dat <-read.csv(here("Data","Raw","ppi_corn_annual.csv"),header = T)

# Assuming ppi_dat is your original dataset with "DATE" and "WPU0121" columns
# Convert DATE to Date format
ppi_dat$DATE <- as.Date(ppi_dat$DATE)
# Extract year from DATE
ppi_dat <- ppi_dat %>%
  mutate(year = lubridate::year(DATE))
# Calculate annual average of WPU0121
ppi_annual <- ppi_dat %>%
  group_by(year) %>%
  summarise(wpu_annual = mean(WPU01220205, na.rm = TRUE))

## Set 1996 ppi as basic
wpu_1996 <- ppi_annual %>% filter(year == 1996) %>% pull(wpu_annual)

###
corn_sel <- corn_ers %>% 
           dplyr::select('Category','Item','Units','Region','Year','Value') %>%
           filter(Item %in% c("Primary product, grain", "Seed","Fertilizer  ","Chemicals",
                              "Total, operating costs","Yield","Price"))

###
corn_sel <- corn_sel %>% filter(Region %in% c("U.S. total","Heartland" , "Northern Great Plains",
                                              "Prairie Gateway" ))

#### #########################
#### 
rev_seed_dat <- corn_sel %>%
  filter(Item %in% c("Primary product, grain", "Yield","Price", "Seed","Total, operating costs"))

# Define custom breaks for the x-axis
custom_breaks <- seq(1996, 2024, by = 4)
#### 
ppi_annual <- ppi_annual %>% filter(year %in% 1996:2023)



# Define common filter criteria
regions <- c("U.S. total", "Heartland", "Northern Great Plains")
items <- c("Primary product, grain", "Seed")

# Create a function to simplify data preparation
prepare_data <- function(data, adjust_ppi = FALSE) {
  data %>%
    filter(Region %in% regions, Item %in% if (adjust_ppi) c(items, "Yield") else items) %>%
    left_join(ppi_annual, by = c("Year" = "year")) %>%
    dplyr::select(Year, Region, Item, Value, wpu_annual) %>%
    spread(Item, Value) %>%
    mutate(
      rev_minus_seed = if (adjust_ppi) {
        wpu_normalized <- wpu_annual / wpu_1996
        (`Primary product, grain` / wpu_normalized) - (Seed / wpu_normalized)
      } else {
        `Primary product, grain` - Seed
      }
    ) %>%
    drop_na()
}

# Prepare data for the two plots
plot1_wide_no_adjust <- prepare_data(rev_seed_dat, adjust_ppi = FALSE)
plot1_wide_adjust <- prepare_data(rev_seed_dat, adjust_ppi = TRUE)

# Create a function to simplify the ggplot generation
create_plot <- function(data, y_label = NULL) {
  ggplot(data, aes(x = Year, y = rev_minus_seed, color = Region, group = Region)) +
    geom_line() +
    scale_color_manual(values = c("Heartland" = "orange", 
                                  "U.S. total" = "brown",
                                  "Northern Great Plains" = "purple")) +
    ylim(100, 1250) +
    labs(
      y = y_label,
      color = "Region"
    ) +
    scale_x_continuous(breaks = seq(1996, 2024, by = 4), limits = c(1996, 2024)) +
    theme_minimal() +
    theme(legend.position = if (!is.null(y_label)) c(0.9, -0.15) else "none",
          legend.direction = "horizontal")
}

# Generate the two plots
rev_minus_seed_no_adjust <- create_plot(plot1_wide_no_adjust, y_label = "Revenue - Seed Cost ($/ac)")
rev_minus_seed_adjust <- create_plot(plot1_wide_adjust)

# Combine the plots
rev_seed_comb <- rev_minus_seed_no_adjust + rev_minus_seed_adjust +
  plot_layout(ncol = 2) +
  plot_annotation(
    title = "Net Revenue After Seed Cost",
    subtitle = "Left: Non-Adjusted | Right: PPI Adjusted",
    theme = theme(
      plot.title = element_text(hjust = 0.5),
      plot.subtitle = element_text(hjust = 0.5),
      plot.margin = margin(t = 10, r = 10, b = 40, l = 10)
    )
  )

ggsave(here("Results","Figures","fig1_rev_after_seed.png"), plot = rev_seed_comb , width = 8, height = 6)



```


## Figure2 (Experimental design Sample)
# [td_figure] / [fig2_trial_design_sample.png]


```{r figure2 experimental design, cache = T, results = "hide"}

 td_sample <-st_read(here("Data","Raw","trial-design-sample.shp"))

# Mutating the trial_rate based on tgt_seed values
td_sample <- td_sample %>%
  mutate(trial_rate = case_when(
    tgt_seed == 130 ~ 32,
    tgt_seed == 145 ~ 30,
    tgt_seed == 110 ~ 28,
    tgt_seed == 90  ~ 34,
    tgt_seed == 160 ~ 36,
    TRUE ~ NA_real_  # If tgt_seed doesn't match any of the above values, assign NA
  )) %>% dplyr::select(trial_rate)

random_colors <- c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00")  # Example colors

td_figure  <- ggplot(td_sample) +
  geom_sf(aes(fill = factor(trial_rate))) +  # Convert trial_rate to a factor for discrete values
  scale_fill_manual(values = random_colors, name = "Trial Seed Rate (K/ac)") +  # Random color scale with custom legend title
  theme_minimal() +
  coord_sf(expand = FALSE) +  # Prevents automatic expansion of the plot
  theme(axis.title = element_blank(),   # Remove axis titles
        axis.text = element_blank(),    # Remove axis text
        axis.ticks = element_blank())   # Remove axis ticks

# Save the plot
ggsave(here("Results","Figures","fig2_trial_design_sample.png"), plot = td_figure, width = 6, height = 4)
```


###################################################
###################################################
Set types of response and estimate profit
###################################################

###################################################
###################################################
Result Figure1  (Opt vs Stq at a given climate ) 
###################################################

```{r Result Figure1 Opt vs Stq at a given climate, cache = T, results = "hide"}

########################

x_min_prec <- min(est_tab2$prcp_tot, na.rm = TRUE)
x_max_prec <- max(est_tab2$prcp_tot, na.rm = TRUE)
y_min_prec <- min(est_tab2$opt_s, est_tab2$stq_s)
y_max_prec <- max(est_tab2$opt_s, est_tab2$stq_s)

opt_stq_prec <- ggplot(est_tab2) +
  geom_point(aes(x = prcp_tot, y = opt_s, color = "EOSR")) +
  geom_point(aes(x = prcp_tot, y = stq_s, color = "SQSR")) +
  scale_color_manual(
    name = "Type",
    values = c("EOSR" = "red", "SQSR" = "blue"),
    labels = c("EOSR", "SQSR")
  ) +
   geom_segment(aes(x = x_min_prec, y = y_min_prec, xend = x_max_prec, yend = y_max_prec), color = "black", size = 0.2) +  # Add diagonal line
labs(  y = "Seeding Rate",
       x = "Precipitation (inch)") +
  theme(legend.position="none",
    axis.text = element_text(size = 14),  # Increase axis text size
    axis.title = element_text(size = 16)  # Increase axis title size
   # plot.title = element_text(size = 18)   # Increase plot title size (if applicable)
  )

x_min_gdd <- min(est_tab2$gdd_tot, na.rm = TRUE)
x_max_gdd <- max(est_tab2$gdd_tot, na.rm = TRUE)
y_min_gdd <- min(est_tab2$opt_s, est_tab2$stq_s)
y_max_gdd <- max(est_tab2$opt_s, est_tab2$stq_s)

opt_stq_gdd <- ggplot(est_tab2) +
  geom_point(aes(x = gdd_tot, y = opt_s, color = "EOSR")) +
  geom_point(aes(x = gdd_tot, y = stq_s, color = "SQSR")) +
  scale_color_manual(
    name = "Seeding Type",
    values = c("EOSR" = "red", "SQSR" = "blue"),
    labels = c("EOSR", "SQSR")
  ) +
   geom_segment(aes(x = x_min_gdd, y = y_min_gdd, xend = x_max_gdd, yend = y_max_gdd), color = "black", size = 0.2) +  # Add diagonal line
labs(  y = NULL,
       x = "Accumulated GDD") +
  theme(
legend.position = c(0.1,-0.3),
legend.direction = "horizontal",
legend.title = element_text(size = 14),  # Increase legend title size
    legend.text = element_text(size = 14),   # Increase legend text size
     axis.title.y = element_blank(),
 axis.text = element_text(size = 14),  # Increase axis text size
 axis.title.x = element_text(size = 16),  # Increase x-axis title size
 plot.margin = margin(5, 5, 60, 5) 
   )


opt_stq_weather <- (opt_stq_prec | opt_stq_gdd) 

opt_stq_weather <- (opt_stq_prec | opt_stq_gdd) + # Collect legends from both plots
  theme(
    plot.margin = margin(10, 10, 40, 10),
    legend.position = c(-0.2,-0.3)
  )


ggsave(here("Figure","opt_stq_weather.png"), plot = opt_stq_weather , width = 16, height = 10, units = "in")

```


## Results Figure3 (Estimated Profit and Yield response by type)) 

```{r  Type A2 figure profit and yield response , cache = T, results = "hide"}

###########################################
## Comparison of profit and yield response vertically
###############


### TYPE A representative 

info_tb_binded
eval_s


est_type_a2 <-est_type_all %>% filter(resp_type=="A2")

est_type_a2$ffy

est_dat_a <- est_type_a2 %>% 
  filter(ffy == "FriestDennis_Dubouis_2023") 

opt_s_ffy_a <- est_dat_a$opt_s
stq_s_ffy_a <- est_dat_a$stq_s

   est_pp_a <-est_dat_a %>%
  unnest(eval_s) %>%  # Unnest if eval_s is a list-column
  mutate(yield_hat = round(yield_hat, 1),
         profit_hat = round((yield_hat * 5.5 - input_rate * 3.81), 1)) %>%
     dplyr::select(input_rate,yield_hat,profit_hat)

# Find two points closest to stq_s and opt_s
stq_s_point_a <-    est_pp_a %>%
  slice(which.min(abs(input_rate - stq_s_ffy_a)))

max_y_point_a <-  est_pp_a %>%
  slice(which.max(yield_hat))

opt_s_point_a <-  est_pp_a %>%
  slice(which.max(profit_hat))


# Define y-axis limits to avoid vertical lines affecting the smooth plot
# Define y-axis limits to avoid vertical lines affecting the smooth plot

y_limits_profit_a <- c(min(est_pp_a$profit_hat, na.rm = TRUE) * 0.98, max(est_pp_a$profit_hat, na.rm = TRUE) * 1.02)  # Adjust as needed

# Create data frame for vertical lines with labels and colors
vline_profit_a <- tibble(
  x = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  y = c(stq_s_point_a$profit_hat, opt_s_point_a$profit_hat, max_y_point_a$profit_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
  #,type = c("dashed", "dashed", "dashed")  # Line type for visual purpose
)

# Create x-axis labels data frame
x_labels_a <- tibble(
  input_rate = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  label = as.character(c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate)),
  color = c("blue", "red", "black")
)

diff_profit_stq_eosr_a <- opt_s_point_a$profit_hat - stq_s_point_a$profit_hat
diff_profit_max_eosr_a <- opt_s_point_a$profit_hat - max_y_point_a$profit_hat

# Create annotations data frame with labels directly on the points
annotations_profit_a <- bind_rows(
  stq_s_point_a %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = sprintf("-$%.1f", diff_profit_stq_eosr_a)
    ),
  opt_s_point_a %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA  # No difference label for EOSR
    ),
  max_y_point_a %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = sprintf("-$%.1f", diff_profit_max_eosr_a)
    )
)

# Create the plot
plot_profit_strong_inc <- ggplot(est_pp_a, aes(x = input_rate, y = profit_hat)) +
  geom_smooth(method = "loess", color = 'yellow') +
  geom_point(data = stq_s_point_a, aes(x = input_rate, y = profit_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_a, aes(x = input_rate, y = profit_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_a, aes(x = input_rate, y = profit_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_profit_a, aes(x = x, xend = x, y = y_limits_profit_a[1]+5, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_profit_a, aes(x = input_rate, y = y_limits_profit_a[1] , 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for profit_hat differences from EOSR
  geom_text(data = filter(annotations_profit_a, !is.na(diff_label)),
            aes(x = input_rate, y = profit_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_profit_a,
                  xlim = c(30,40)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
  
  # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Profit ($/ac)")

# Display the plot
print(plot_profit_strong_inc)


# Define y-axis limits for yield plot
y_limits_yield_a <- c(min(est_pp_a$yield_hat, na.rm = TRUE) * 0.98, max(est_pp_a$yield_hat, na.rm = TRUE) * 1.02)

# Create data frame for vertical lines with labels and colors for yield
vline_yield_a <- tibble(
  x = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  y = c(stq_s_point_a$yield_hat, opt_s_point_a$yield_hat, max_y_point_a$yield_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
)


diff_yield_stq_eosr_a <- stq_s_point_a$yield_hat - opt_s_point_a$yield_hat 
diff_yield_max_eosr_a <- max_y_point_a$yield_hat - opt_s_point_a$yield_hat 



# Create annotations data frame for yield
annotations_yield_a <- bind_rows(
  stq_s_point_a %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = paste0(sprintf("%.1f", diff_yield_stq_eosr_a)," bu")  # Use yield differences if available
    ),
  opt_s_point_a %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA
    ),
  max_y_point_a %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = paste0(sprintf("%.1f", diff_yield_max_eosr_a)," bu")  # Use yield differences if available
    )
)




# Create the yield plot
plot_yield_strong_inc <- ggplot(est_pp_a, aes(x = input_rate, y = yield_hat)) +
  geom_smooth(method = "loess", color = 'green') +
  geom_point(data = stq_s_point_a, aes(x = input_rate, y = yield_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_a, aes(x = input_rate, y = yield_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_a, aes(x = input_rate, y = yield_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_yield_a, aes(x = x, xend = x, y = y_limits_yield_a[1] +4, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_yield_a, aes(x = input_rate, y = y_limits_yield_a[1]+1, 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for yield_hat differences from EOSR
  geom_text(data = filter(annotations_yield_a, !is.na(diff_label)),
            aes(x = input_rate, y = yield_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_yield_a,
                  xlim = c(30,40)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
  
  # Remove the legend
 # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Yield (units/ac)")

# Combine both plots vertically
type_a2_response_plot <- plot_yield_strong_inc | plot_profit_strong_inc 

# Display the combined plot






###################################################
###################################################
# Result Figure2(dif_pro_seed_comb ; Diff Profit at a given climate)
###################################################

```{r Result Figure2 Diff Profit at a given climate, cache = T, results = "hide"}


not_in_fig2 <-c('eval_s', 'quad_fit', 'coef_quad', 'b', 'a', 'c', 'f_dv', 's_dv', 'ymsr')

est_fig2 <- est_type_all %>% dplyr::select(-all_of(not_in_fig2))

# Grouping by prcp_tot for dif_pro_seed
est_fig2$prcp_group <- cut(
  est_tab2$prcp_tot,
  breaks = quantile(est_fig2$prcp_tot, probs = 0:10 / 10, na.rm = TRUE),
  include.lowest = TRUE
)

# Define colors for each prcp_group using a blue color scale
group_colors_prec <- colorRampPalette(brewer.pal(9, "Blues"))(10)  # 10 shades of blue

# Define labels for the legend based on numeric ranges
group_labels_prec <- levels(est_fig2$prcp_group)

# Plot for prcp_tot
dif_pro_seed_prec <- ggplot(est_fig2) +
  geom_point(aes(x = dif_s, y = dif_p, color = prcp_group),size = 3) + scale_color_manual(
    name = "Precipitation (inch)",  # Legend title with two lines
    values = group_colors_prec,  # Colors for each prcp_group
    breaks = group_labels_prec,  # Display the actual ranges in the legend
    labels = group_labels_prec,  # Use numeric ranges as labels
     guide = guide_legend(ncol = 1)
  ) +
   geom_segment(aes(x = 0, y = -100, xend = 0, yend = 0), color = "black", size = 0.5,
                linetype='dashed') +  # Add vertical line
  scale_x_continuous(
    breaks = seq(floor(min(est_tab2$dif_s, na.rm = TRUE) / 5) * 5,
                 ceiling(max(est_tab2$dif_s, na.rm = TRUE) / 5) * 5,
                 by = 5)  # Set breaks every 5 units
  ) +
  ylim(-100, 0) +  # Set y-axis limits
  labs(
    x = NULL,
    y = "Estimated Profit Difference($/ac)"
  ) +
  theme(
    legend.position = "right", 
    legend.direction = 'vertical',# Place the legend at the bottom
      axis.text = element_text(size = 16),  # Increase axis text size
    axis.title = element_text(size = 16),  # Increase axis title size
    legend.title = element_text(size = 16),  # Increase legend title font size
    legend.text = element_text(size = 16)    # Increase legend text font size
  )

# Grouping by resp_type for dif_pro_seed_type
est_fig2$resp_type <- factor(est_fig2$resp_type, levels = c('A1', 'A2', 'B1',"B2","C"))

# Define colors for each resp_type using Viridis color scale
group_colors_resp <- viridis(5)  # Viridis color scale with 4 colors

# Define labels for the legend based on resp_type values
group_labels_resp <- levels(est_fig2$resp_type)

# Plot for resp_type
dif_pro_seed_type <- ggplot(est_fig2) +
  geom_point(aes(x = dif_s, y = dif_p, color = resp_type),size=3) +
  scale_color_manual(
    name = "Response Type",  # Legend title
    values = group_colors_resp,  # Colors for each resp_type
    breaks = group_labels_resp,  # Display the actual values in the legend
    labels = group_labels_resp,
    guide = guide_legend(ncol = 1)# Use resp_type values as labels
  ) +
   geom_segment(aes(x = 0, y = -100, xend = 0, yend = 0), color = "black", size = 0.5,
                linetype='dashed') +  # Add vertical line
  scale_x_continuous(
    breaks = seq(floor(min(est_fig2$dif_s, na.rm = TRUE) / 5) * 5,
                 ceiling(max(est_fig2$dif_s, na.rm = TRUE) / 5) * 5,
                 by = 5)  # Set breaks every 5 units
  ) +
  ylim(-100, 0) +  # Set y-axis limits
  labs(
    x = "SQSR - EOSR (K/ac)",
    y = "Estimated Profit Difference($/ac)"
  ) +
  theme(
    legend.position = "right",
    legend.direction = "vertical",# Place the legend at the bottom
     axis.title.x =  element_text(size = 16),
    axis.text = element_text(size = 16),  # Increase axis text size
 axis.title.y = element_text(size = 16),  # Increase x-axis title size
    legend.title = element_text(size = 16),  # Increase legend title font size
    legend.text = element_text(size = 16)    # Increase legend text font size
  )

# Combine the two plots side by side with patchwork
dif_pro_seed_comb <- (dif_pro_seed_prec / dif_pro_seed_type)   # Collect legends to appear only once


ggsave(here("Figure","dif_pro_seed_comb.png"), plot = dif_pro_seed_comb , width = 14, height = 12, units = "in")


```



###################################################
###################################################
  Type A,B,C figure ( type_resp_combined ; profit and yield response by types)
###################################################
###################################################

```{r  Type A2 figure profit and yield response , cache = T, results = "hide"}

###########################################
## Comparison of profit and yield response vertically
###############


### TYPE A representative 

est_type_a2 <-est_type_all %>% filter(resp_type=="A2")

est_type_a2$ffy

est_dat_a <- est_type_a2 %>% 
  filter(ffy == "FriestDennis_Dubouis_2023") 

opt_s_ffy_a <- est_dat_a$opt_s
stq_s_ffy_a <- est_dat_a$stq_s

   est_pp_a <-est_dat_a %>%
  unnest(eval_s) %>%  # Unnest if eval_s is a list-column
  mutate(yield_hat = round(yield_hat, 1),
         profit_hat = round((yield_hat * 5.5 - input_rate * 3.81), 1)) %>%
     dplyr::select(input_rate,yield_hat,profit_hat)

# Find two points closest to stq_s and opt_s
stq_s_point_a <-    est_pp_a %>%
  slice(which.min(abs(input_rate - stq_s_ffy_a)))

max_y_point_a <-  est_pp_a %>%
  slice(which.max(yield_hat))

opt_s_point_a <-  est_pp_a %>%
  slice(which.max(profit_hat))


# Define y-axis limits to avoid vertical lines affecting the smooth plot
# Define y-axis limits to avoid vertical lines affecting the smooth plot

y_limits_profit_a <- c(min(est_pp_a$profit_hat, na.rm = TRUE) * 0.98, max(est_pp_a$profit_hat, na.rm = TRUE) * 1.02)  # Adjust as needed

# Create data frame for vertical lines with labels and colors
vline_profit_a <- tibble(
  x = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  y = c(stq_s_point_a$profit_hat, opt_s_point_a$profit_hat, max_y_point_a$profit_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
  #,type = c("dashed", "dashed", "dashed")  # Line type for visual purpose
)

# Create x-axis labels data frame
x_labels_a <- tibble(
  input_rate = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  label = as.character(c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate)),
  color = c("blue", "red", "black")
)

diff_profit_stq_eosr_a <- opt_s_point_a$profit_hat - stq_s_point_a$profit_hat
diff_profit_max_eosr_a <- opt_s_point_a$profit_hat - max_y_point_a$profit_hat

# Create annotations data frame with labels directly on the points
annotations_profit_a <- bind_rows(
  stq_s_point_a %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = sprintf("-$%.1f", diff_profit_stq_eosr_a)
    ),
  opt_s_point_a %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA  # No difference label for EOSR
    ),
  max_y_point_a %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = sprintf("-$%.1f", diff_profit_max_eosr_a)
    )
)

# Create the plot
plot_profit_strong_inc <- ggplot(est_pp_a, aes(x = input_rate, y = profit_hat)) +
  geom_smooth(method = "loess", color = 'yellow') +
  geom_point(data = stq_s_point_a, aes(x = input_rate, y = profit_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_a, aes(x = input_rate, y = profit_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_a, aes(x = input_rate, y = profit_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_profit_a, aes(x = x, xend = x, y = y_limits_profit_a[1]+5, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_profit_a, aes(x = input_rate, y = y_limits_profit_a[1] , 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for profit_hat differences from EOSR
  geom_text(data = filter(annotations_profit_a, !is.na(diff_label)),
            aes(x = input_rate, y = profit_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_profit_a,
                  xlim = c(30,40)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
  
  # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Profit ($/ac)")

# Display the plot
print(plot_profit_strong_inc)


# Define y-axis limits for yield plot
y_limits_yield_a <- c(min(est_pp_a$yield_hat, na.rm = TRUE) * 0.98, max(est_pp_a$yield_hat, na.rm = TRUE) * 1.02)

# Create data frame for vertical lines with labels and colors for yield
vline_yield_a <- tibble(
  x = c(stq_s_point_a$input_rate, opt_s_point_a$input_rate, max_y_point_a$input_rate),
  y = c(stq_s_point_a$yield_hat, opt_s_point_a$yield_hat, max_y_point_a$yield_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
)


diff_yield_stq_eosr_a <- stq_s_point_a$yield_hat - opt_s_point_a$yield_hat 
diff_yield_max_eosr_a <- max_y_point_a$yield_hat - opt_s_point_a$yield_hat 



# Create annotations data frame for yield
annotations_yield_a <- bind_rows(
  stq_s_point_a %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = paste0(sprintf("%.1f", diff_yield_stq_eosr_a)," bu")  # Use yield differences if available
    ),
  opt_s_point_a %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA
    ),
  max_y_point_a %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = paste0(sprintf("%.1f", diff_yield_max_eosr_a)," bu")  # Use yield differences if available
    )
)




# Create the yield plot
plot_yield_strong_inc <- ggplot(est_pp_a, aes(x = input_rate, y = yield_hat)) +
  geom_smooth(method = "loess", color = 'green') +
  geom_point(data = stq_s_point_a, aes(x = input_rate, y = yield_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_a, aes(x = input_rate, y = yield_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_a, aes(x = input_rate, y = yield_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_yield_a, aes(x = x, xend = x, y = y_limits_yield_a[1] +4, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_yield_a, aes(x = input_rate, y = y_limits_yield_a[1]+1, 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for yield_hat differences from EOSR
  geom_text(data = filter(annotations_yield_a, !is.na(diff_label)),
            aes(x = input_rate, y = yield_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_yield_a,
                  xlim = c(30,40)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
  
  # Remove the legend
 # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Yield (units/ac)")

# Combine both plots vertically
type_a2_response_plot <- plot_yield_strong_inc | plot_profit_strong_inc 

# Display the combined plot



```

```{r  Type B2 figure profit and yield response , cache = T, results = "hide"}

est_type_b2 <-est_type_all %>% filter(resp_type=="B2")

est_type_b2$ffy


est_dat_b <- est_type_b2 %>% 
  filter(ffy == "Nelson_Wirth_2022") 

opt_s_ffy_b <- est_dat_b$opt_s
stq_s_ffy_b <- est_dat_b$stq_s

   est_pp_b <-est_dat_b %>%
  unnest(eval_s) %>%  # Unnest if eval_s is a list-column
  mutate(yield_hat = round(yield_hat, 1),
         profit_hat = round((yield_hat * 5.5 - input_rate * 3.81), 1)) %>%
     dplyr::select(input_rate,yield_hat,profit_hat)

# Find two points closest to stq_s and opt_s
stq_s_point_b <-    est_pp_b %>%
  slice(which.min(abs(input_rate - stq_s_ffy)))

max_y_point_b <-  est_pp_b %>%
  slice(which.max(yield_hat))

opt_s_point_b <-  est_pp_b %>%
  slice(which.max(profit_hat))


# Define y-axis limits to avoid vertical lines affecting the smooth plot
# Define y-axis limits to avoid vertical lines affecting the smooth plot

y_limits_profit_b <- c(min(est_pp_b$profit_hat, na.rm = TRUE) * 0.98, max(est_pp_b$profit_hat, na.rm = TRUE) * 1.02)  # Adjust as needed

# Create data frame for vertical lines with labels and colors
vline_profit_b <- tibble(
  x = c(stq_s_point_b$input_rate, opt_s_point_b$input_rate, max_y_point_b$input_rate),
  y = c(stq_s_point_b$profit_hat, opt_s_point_b$profit_hat, max_y_point_b$profit_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
  #,type = c("dashed", "dashed", "dashed")  # Line type for visual purpose
)

# Create x-axis labels data frame
x_labels_b <- tibble(
  input_rate = c(stq_s_point_b$input_rate, opt_s_point_b$input_rate, max_y_point_b$input_rate),
  label = as.character(c(stq_s_point_b$input_rate, opt_s_point_b$input_rate, max_y_point_b$input_rate)),
  color = c("blue", "red", "black")
)

diff_profit_stq_eosr_b <- opt_s_point_b$profit_hat - stq_s_point_b$profit_hat
diff_profit_max_eosr_b <- opt_s_point_b$profit_hat - max_y_point_b$profit_hat

# Create annotations data frame with labels directly on the points
annotations_profit_b <- bind_rows(
  stq_s_point %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = sprintf("-$%.1f", diff_profit_stq_eosr_b)
    ),
  opt_s_point_b %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA  # No difference label for EOSR
    ),
  max_y_point_b %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = sprintf("-$%.1f", diff_profit_max_eosr_b)
    )
)

# Create the plot
plot_profit_plateau_inc1 <- ggplot(est_pp_b, aes(x = input_rate, y = profit_hat)) +
  geom_smooth(method = "loess", color = 'yellow') +
  geom_point(data = stq_s_point_b, aes(x = input_rate, y = profit_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_b, aes(x = input_rate, y = profit_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_b, aes(x = input_rate, y = profit_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_profit_b, aes(x = x, xend = x, y = y_limits_profit_b[1]+15, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_profit_b, aes(x = input_rate, y = y_limits_profit_b[1] , 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for profit_hat differences from EOSR
  geom_text(data = filter(annotations_profit_b, !is.na(diff_label)),
            aes(x = input_rate, y = profit_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_profit_b,
                  xlim = c(27.5,37.5)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
  # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Profit ($/ac)")


# Define y-axis limits for yield plot
y_limits_yield_b <- c(min(est_pp_b$yield_hat, na.rm = TRUE) * 0.98, max(est_pp_b$yield_hat, na.rm = TRUE) * 1.02)

# Create data frame for vertical lines with labels and colors for yield
vline_yield_b <- tibble(
  x = c(stq_s_point_b$input_rate, opt_s_point_b$input_rate, max_y_point_b$input_rate),
  y = c(stq_s_point_b$yield_hat, opt_s_point_b$yield_hat, max_y_point_b$yield_hat),
  color = c("blue", "red", "black"),
  label = c("SQSR", "EOSR", "YMSR")
)


diff_yield_stq_eosr_b <- stq_s_point_b$yield_hat - opt_s_point_b$yield_hat 
diff_yield_max_eosr_b <- max_y_point_b$yield_hat - opt_s_point_b$yield_hat 



# Create annotations data frame for yield
annotations_yield_b <- bind_rows(
  stq_s_point %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = paste0(sprintf("%.1f", diff_yield_stq_eosr_b)," bu")  # Use yield differences if available
    ),
  opt_s_point_b %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA
    ),
  max_y_point_b %>%
    mutate(
      abrv = paste("YMSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "YMSR",
      color = "black",
      diff_label = paste0(sprintf("%.1f", diff_yield_max_eosr_b)," bu")  # Use yield differences if available
    )
)

# Create the yield plot
plot_yield_plateau_inc1 <- ggplot(est_pp_b, aes(x = input_rate, y = yield_hat)) +
  geom_smooth(method = "loess", color = 'green') +
  geom_point(data = stq_s_point_b, aes(x = input_rate, y = yield_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_b, aes(x = input_rate, y = yield_hat), color = "red", size = 1.5) +
  geom_point(data = max_y_point_b, aes(x = input_rate, y = yield_hat), color = "black", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_yield_b, aes(x = x, xend = x, y = y_limits_yield_b[1] +4, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_yield_b, aes(x = input_rate, y = y_limits_yield_b[1]+1, 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for yield_hat differences from EOSR
  geom_text(data = filter(annotations_yield_b, !is.na(diff_label)),
            aes(x = input_rate, y = yield_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_yield_b,
                  xlim = c(27.5,37.5)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red", "YMSR" = "black")) +
   # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Yield (K/ac)")

print(plot_yield_plateau_inc1)



type_b2_response_plot <-  plot_yield_plateau_inc1 | plot_profit_plateau_inc1 

```

```{r Type A1,B1 figure profit and yield response , cache = T, results = "hide"}
## (concave and down)
# 'Nelson_DJWest_2023'

## Problematic field 
## 'CLC_ManfredJohnson_2023'

est_type_a1 <- est_type_all %>% filter(resp_type=="A1")
est_type_a1$ffy

est_type_b1 <- est_type_all %>% filter(resp_type=="B1")
est_type_b1$ffy


est_dat_a1 <- est_type_a1 %>% filter(ffy == 'Gingerich_Field1_2022')

opt_s_ffy_a1 <- est_dat_a1$opt_s
stq_s_ffy_a1 <- est_dat_a1$stq_s

   est_pp_a1 <-est_dat_a1 %>%
  unnest(eval_s) %>%  # Unnest if eval_s is a list-column
  mutate(yield_hat = round(yield_hat, 1),
         profit_hat = round((yield_hat * 5.5 - input_rate * 3.81), 1)) %>%
     dplyr::select(input_rate,yield_hat,profit_hat)

# Find two points closest to stq_s and opt_s
stq_s_point_a1 <-    est_pp_a1 %>%
  slice(which.min(abs(input_rate - stq_s_ffy_a1)))

opt_s_point_a1 <-  est_pp_a1 %>%
  slice(which.max(profit_hat))


# Define y-axis limits to avoid vertical lines affecting the smooth plot
# Define y-axis limits to avoid vertical lines affecting the smooth plot

y_limits_profit_a1 <- c(min(est_pp_a1$profit_hat, na.rm = TRUE) * 0.98, max(est_pp_a1$profit_hat, na.rm = TRUE) * 1.02)  # Adjust as needed

# Create data frame for vertical lines with labels and colors
vline_profit_a1 <- tibble(
  x = c(stq_s_point_a1$input_rate, opt_s_point_a1$input_rate),
  y = c(stq_s_point_a1$profit_hat, opt_s_point_a1$profit_hat),
  color = c("blue", "red"),
  label = c("SQSR", "EOSR")
  #,type = c("dashed", "dashed", "dashed")  # Line type for visual purpose
)

# Create x-axis labels data frame
x_labels_a <- tibble(
  input_rate = c(stq_s_point_a1$input_rate, opt_s_point_a1$input_rate),
  label = as.character(c(stq_s_point_a1$input_rate, opt_s_point_a1$input_rate)),
  color = c("blue", "red")
)

diff_profit_stq_eosr_a1 <- opt_s_point_a1$profit_hat - stq_s_point_a1$profit_hat

# Create annotations data frame with labels directly on the points
annotations_profit_a1 <- bind_rows(
  stq_s_point_a1 %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = sprintf("-$%.1f", diff_profit_stq_eosr_a1)
    ),
  opt_s_point_a1 %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA  # No difference label for EOSR
    )
)

# Create the plot
plot_profit_a1 <- ggplot(est_pp_a1, aes(x = input_rate, y = profit_hat)) +
  geom_smooth(method = "loess", color = 'yellow') +
  geom_point(data = stq_s_point_a1, aes(x = input_rate, y = profit_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_a1, aes(x = input_rate, y = profit_hat), color = "red", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_profit_a1, aes(x = x, xend = x, y = y_limits_profit_a1[1]+5, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_profit_a1, aes(x = input_rate, y = y_limits_profit_a1[1] , 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for profit_hat differences from EOSR
  geom_text(data = filter(annotations_profit_a1, !is.na(diff_label)),
            aes(x = input_rate, y = profit_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_profit_a1,
                  xlim = c(30,40)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red")) +
  
  # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Profit ($/ac)")




est_dat_b1 <- est_type_b1 %>% filter(ffy == 'CLC_CorralsEast_2022')

opt_s_ffy_b1 <- est_dat_b1$opt_s
stq_s_ffy_b1 <- est_dat_b1$stq_s

   est_pp_b1 <-est_dat_b1 %>%
  unnest(eval_s) %>%  # Unnest if eval_s is a list-column
  mutate(yield_hat = round(yield_hat, 1),
         profit_hat = round((yield_hat * 5.5 - input_rate * 3.81), 1)) %>%
     dplyr::select(input_rate,yield_hat,profit_hat)

# Find two points closest to stq_s and opt_s
stq_s_point_b1 <-    est_pp_b1 %>%
  slice(which.min(abs(input_rate - stq_s_ffy_b1)))

opt_s_point_b1 <-  est_pp_b1 %>%
  slice(which.max(profit_hat))


# Define y-axis limits to avoid vertical lines affecting the smooth plot
# Define y-axis limits to avoid vertical lines affecting the smooth plot

y_limits_profit_b1 <- c(min(est_pp_b1$profit_hat, na.rm = TRUE) * 0.98, max(est_pp_b1$profit_hat, na.rm = TRUE) * 1.02)  # Adjust as needed

# Create data frame for vertical lines with labels and colors
vline_profit_b1 <- tibble(
  x = c(stq_s_point_b1$input_rate, opt_s_point_b1$input_rate),
  y = c(stq_s_point_b1$profit_hat, opt_s_point_b1$profit_hat),
  color = c("blue", "red"),
  label = c("SQSR", "EOSR")
  #,type = c("dashed", "dashed", "dashed")  # Line type for visual purpose
)

# Create x-axis labels data frame
x_labels_a <- tibble(
  input_rate = c(stq_s_point_b1$input_rate, opt_s_point_b1$input_rate),
  label = as.character(c(stq_s_point_b1$input_rate, opt_s_point_b1$input_rate)),
  color = c("blue", "red")
)

diff_profit_stq_eosr_b1 <- opt_s_point_b1$profit_hat - stq_s_point_b1$profit_hat

# Create annotations data frame with labels directly on the points
annotations_profit_b1 <- bind_rows(
  stq_s_point_b1 %>%
    mutate(
      abrv = paste("SQSR", "\n","(", as.character(round(input_rate,1)), ")"),
      label = "SQSR",
      color = "blue",
      diff_label = sprintf("-$%.1f", diff_profit_stq_eosr_b1)
    ),
  opt_s_point_b1 %>%
    mutate(
      abrv = paste("EOSR", "\n", "(", as.character(round(input_rate,1)), ")"),
      label = "EOSR",
      color = "red",
      diff_label = NA  # No difference label for EOSR
    )
)

# Create the plot
plot_profit_b1 <- ggplot(est_pp_b1, aes(x = input_rate, y = profit_hat)) +
  geom_smooth(method = "loess", color = 'yellow') +
  geom_point(data = stq_s_point_b1, aes(x = input_rate, y = profit_hat), color = "blue", size = 1.5) +
  geom_point(data = opt_s_point_b1, aes(x = input_rate, y = profit_hat), color = "red", size = 1.5) +
  
  # Draw vertical lines with dashed linetype and specified y-axis limits
  geom_segment(data = vline_profit_b1, aes(x = x, xend = x, y = y_limits_profit_b1[1]+5, yend = y, color = label), 
               linetype = "dashed") +
  
  # Add text annotations for points
  geom_text(data = annotations_profit_b1, aes(x = input_rate, y = y_limits_profit_b1[1] , 
                                           label = abrv, color = label), 
            vjust = 0, hjust = 0.5, size = 4) +
  
  # Add text annotations for profit_hat differences from EOSR
  geom_text(data = filter(annotations_profit_b1, !is.na(diff_label)),
            aes(x = input_rate, y = profit_hat, label = diff_label, color = label), 
            vjust = -1, hjust = 0.5, size = 4, fontface = "italic") +
  
  # Set y-axis limits to avoid interference from vertical lines
  coord_cartesian(ylim = y_limits_profit_b1,
                  xlim = c(17.5,30)) +
  
  # Set the color scale for the plot (no legend)
  scale_color_manual(values = c("SQSR" = "blue", "EOSR" = "red")) +
  
  # Remove the legend
   theme(
    axis.title.x = element_text(size = 18),  # Increase font size for x-axis label
    axis.title.y = element_text(size = 18),  # Increase font size for y-axis label
    axis.text.x = element_text(size = 18),    # Increase font size for x-axis numeric values
    axis.text.y = element_text(size = 18) ,    # Increase font size for y-axis numeric values
     legend.position = "none") +
  
  # Customize labels
  labs( x = "Seeding Rate (K/ac)", y = "Estimated Profit ($/ac)")


type_a1_b1_response_plot <- plot_profit_a1 | plot_profit_b1 


 
```

```{r all Type combined figure , cache = T, results = "hide"}

# Add captions to the combined plot using patchwork's plot_annotation


# Create individual captions for each subplot
caption_a2 <- ggplot() + 
  annotate("text", x = 0.5, y = 0.5, label = "[Type A2]  EOSR > SQSR & Concave &  EOSR  YMSR", 
           size = 8, hjust = 0.5, vjust = 0.5) + 
  theme_void()

caption_b2 <- ggplot() + 
  annotate("text", x = 0.5, y = 0.5, label = "[Type B2]  EOSR < SQSR & Concave &  EOSR  YMSR", 
           size = 8, hjust = 0.5, vjust = 0.5) + 
  theme_void()

caption_a1_b1 <- ggplot() + 
  annotate("text", x = 0.5, y = 0.5, label = "[Type A1 & B1] Concave &  EOSR = YMSR", 
           size = 8, hjust = 0.5, vjust = 0.5) + 
  theme_void()

# Arrange the plots in a 3x2 grid with captions below each type of plot
type_all_response_plot <- (
  type_a2_response_plot / caption_a2 / 
  type_b2_response_plot / caption_b2 / 
  type_a1_b1_response_plot / caption_a1_b1
) + plot_layout(ncol = 1, heights = c(6, 1, 6, 1,6, 1))

# Display the combined plot
print(type_all_response_plot)

# Save the combined plot as a PNG file
ggsave(here("Figure","type_all_response_plot.png"), 
       plot = type_all_response_plot, 
       width = 15, height = 18, dpi = 300)

```


######################################
############################
10 year Historical price ratio changes scenario
############################
######################################

c_prices <- c(5.5, 3.8, 3.6, 3.7, 3.9, 3.6, 5.7, 6.9, 5.6, 4.3)
s_prices <- c(3.8, 3.4, 3.3, 3.2, 2.9, 3.1, 3.2, 3.4, 3.6, 3.4)

```{r 10year Historical price ratio changes scenario , cache = T, results = "hide"}


# 3.6 , 3.3 ( 3 in the list, highest seed cost ratio)
# 6.9, 3.4 (8 in the list, lowest seed cost ratio)

########################

est_bind_list <- readRDS(here("Data/analysis_results_at_hist_price_0829_24.RDS"))

daymet30_list <-readRDS(here("Data","daymet_30_list_0904_24.rds"))
daymet_list<-readRDS(here("Data","daymet_t_list_0904_24.rds"))

daymet_30 <-bind_rows(daymet30_list)
daymet_t <-bind_rows(daymet_list)




est_price3 <-est_bind_list[[3]]

est_price3 <- est_price3 %>%
  mutate(dif_s = stq_s - opt_s,
         dif_p = stq_p - opt_p,
         dif_y = stq_y - opt_y)

daymet_t_price3 <- daymet_t[daymet_t$ffy %in% est_price3$ffy, ]

est_price3_day <-left_join(est_price3,daymet_t_price3, by = 'ffy')


est_price3_day <- est_price3_day %>%
  mutate(
    yield = map_dbl(eval_s, ~ mean(.x$yield_hat, na.rm = TRUE))
  ) %>% dplyr::select(-weather) %>%
   mutate(gdd_tot = round(gdd_tot,0),
          prcp_tot = round(prcp_tot,0))

 
est_type_all_price3  <- est_price3_day  %>%
  dplyr::select(ffy, opt_s,stq_s,dif_s, dif_p, dif_y, eval_s,farm_id,year,
                gdd_tot,prcp_tot) %>%
 mutate(
    # Apply quadratic fit to each element in eval_s using map
    quad_fit = map(eval_s, ~ lm(yield_hat ~ input_rate + I(input_rate^2), data = .x)),
    
    # Extract coefficients (a, b, c) from the quadratic fit using map
    coef_quad = map(quad_fit, coef),
    # Extract individual coefficients for each fit
    b = map_dbl(coef_quad, ~ .x[2]),  # Coefficient of input_rate (b)
    a = map_dbl(coef_quad, ~ .x[3]),  # Coefficient of input_rate^2 (a)
    c = map_dbl(coef_quad, ~ .x[1]),  # Intercept (c)
    
    # Calculate first and second derivatives
    f_dv = pmap_dbl(list(a, b, opt_s), ~ 2 * ..1 * ..3 + ..2),  # First derivative: 2a * opt_s + b
    s_dv = map_dbl(a, ~ 2 * .x),  # Second derivative: 2a
    
     # Find the input_rate that maximizes yield_hat for each group
    ymsr = map_dbl(eval_s, ~ .x$input_rate[which.max(.x$yield_hat)]),  # ysmr is the input_rate at max yield_hat
    
    # Assign rest_type based on conditions
    resp_type = case_when(
      dif_s < 0 & a < 0 & ymsr == opt_s ~ "A1", #under_seed & corner sol
       dif_s < 0 & a < 0 & ymsr != opt_s ~ "A2",
      dif_s > 0 & a < 0& ymsr == opt_s ~ "B1", #over_seed & corner sol
       dif_s > 0 & a < 0& ymsr != opt_s ~ "B2", #over_seed & corner sol
        a > 0 ~ "C"
    )
  )




not_in_price3 <-c('eval_s', 'quad_fit', 'coef_quad', 'b', 'a', 'c', 'f_dv', 's_dv', 'ymsr')

est_fig_price3  <- est_type_all_price3  %>% dplyr::select(-all_of(not_in_price3))


# Grouping by resp_type for dif_pro_seed_type
est_fig_price3$resp_type <- factor(est_fig_price3$resp_type, levels = c('A1', 'A2', 'B1',"B2","C"))

# Define colors for each resp_type using Viridis color scale
group_colors_resp3 <- viridis(5)  # Viridis color scale with 4 colors

# Define labels for the legend based on resp_type values
group_labels_resp3 <- levels(est_fig_price3$resp_type)

# Plot for resp_type
dif_pro_seed_type_price3 <- ggplot(est_fig_price3 ) +
  geom_point(aes(x = dif_s, y = dif_p, color = resp_type),size=3) +
  scale_color_manual(
    name = "Response Type",  # Legend title
    values = group_colors_resp3,  # Colors for each resp_type
    breaks = group_labels_resp3,  # Display the actual values in the legend
    labels = group_labels_resp3,
    guide = guide_legend(ncol = 1)# Use resp_type values as labels
  ) +
   geom_segment(aes(x = 0, y = -100, xend = 0, yend = 0), color = "black", size = 0.5,
                linetype='dashed') +  # Add vertical line
  scale_x_continuous(
    breaks = seq(floor(min(est_fig_price3 $dif_s, na.rm = TRUE) / 5) * 5,
                 ceiling(max(est_fig_price3 $dif_s, na.rm = TRUE) / 5) * 5,
                 by = 5)  # Set breaks every 5 units
  ) +
  ylim(-100, 0) +  # Set y-axis limits
  labs(
    x = "SQSR - EOSR (K/ac)",
    y = "Estimated Profit Difference($/ac)"
  ) +
  theme(
    legend.position = "right",
    legend.direction = "vertical",# Place the legend at the bottom
     axis.title.x =  element_text(size = 16),
    axis.text = element_text(size = 16),  # Increase axis text size
 axis.title.y = element_text(size = 16),  # Increase x-axis title size
    legend.title = element_text(size = 16),  # Increase legend title font size
    legend.text = element_text(size = 16)    # Increase legend text font size
  )




est_price8 <-est_bind_list[[8]]

est_price8 <- est_price8 %>%
  mutate(dif_s = stq_s - opt_s,
         dif_p = stq_p - opt_p,
         dif_y = stq_y - opt_y)


daymet_t_price8 <- daymet_t[daymet_t$ffy %in% est_price8$ffy, ]

est_price8_day <-left_join(est_price8,daymet_t_price8, by = 'ffy')


est_price8_day <- est_price8_day %>%
  mutate(
    yield = map_dbl(eval_s, ~ mean(.x$yield_hat, na.rm = TRUE))
  ) %>% dplyr::select(-weather) %>%
   mutate(gdd_tot = round(gdd_tot,0),
          prcp_tot = round(prcp_tot,0))

 
est_type_all_price8  <- est_price8_day  %>%
  dplyr::select(ffy, opt_s,stq_s,dif_s, dif_p, dif_y, eval_s,farm_id,year,
                gdd_tot,prcp_tot) %>%
 mutate(
    # Apply quadratic fit to each element in eval_s using map
    quad_fit = map(eval_s, ~ lm(yield_hat ~ input_rate + I(input_rate^2), data = .x)),
    
    # Extract coefficients (a, b, c) from the quadratic fit using map
    coef_quad = map(quad_fit, coef),
    # Extract individual coefficients for each fit
    b = map_dbl(coef_quad, ~ .x[2]),  # Coefficient of input_rate (b)
    a = map_dbl(coef_quad, ~ .x[3]),  # Coefficient of input_rate^2 (a)
    c = map_dbl(coef_quad, ~ .x[1]),  # Intercept (c)
    
    # Calculate first and second derivatives
    f_dv = pmap_dbl(list(a, b, opt_s), ~ 2 * ..1 * ..3 + ..2),  # First derivative: 2a * opt_s + b
    s_dv = map_dbl(a, ~ 2 * .x),  # Second derivative: 2a
    
     # Find the input_rate that maximizes yield_hat for each group
    ymsr = map_dbl(eval_s, ~ .x$input_rate[which.max(.x$yield_hat)]),  # ysmr is the input_rate at max yield_hat
    
    # Assign rest_type based on conditions
    resp_type = case_when(
      dif_s < 0 & a < 0 & ymsr == opt_s ~ "A1", #under_seed & corner sol
       dif_s < 0 & a < 0 & ymsr != opt_s ~ "A2",
      dif_s > 0 & a < 0& ymsr == opt_s ~ "B1", #over_seed & corner sol
       dif_s > 0 & a < 0& ymsr != opt_s ~ "B2", #over_seed & corner sol
        a > 0 ~ "C"
    )
  )




not_in_price8 <-c('eval_s', 'quad_fit', 'coef_quad', 'b', 'a', 'c', 'f_dv', 's_dv', 'ymsr')

est_fig_price8  <- est_type_all_price8  %>% dplyr::select(-all_of(not_in_price8))


# Grouping by resp_type for dif_pro_seed_type
est_fig_price8$resp_type <- factor(est_fig_price8$resp_type, levels = c('A1', 'A2', 'B1',"B2","C"))

# Define colors for each resp_type using Viridis color scale
group_colors_resp8 <- viridis(5)  # Viridis color scale with 4 colors

# Define labels for the legend based on resp_type values
group_labels_resp8 <- levels(est_fig_price8$resp_type)

# Plot for resp_type
dif_pro_seed_type_price8 <- ggplot(est_fig_price8) +
  geom_point(aes(x = dif_s, y = dif_p, color = resp_type),size=3) +
  scale_color_manual(
    name = "Response Type",  # Legend title
    values = group_colors_resp8,  # Colors for each resp_type
    breaks = group_labels_resp8,  # Display the actual values in the legend
    labels = group_labels_resp8,
    guide = guide_legend(ncol = 1)# Use resp_type values as labels
  ) +
   geom_segment(aes(x = 0, y = -100, xend = 0, yend = 0), color = "black", size = 0.5,
                linetype='dashed') +  # Add vertical line
  scale_x_continuous(
    breaks = seq(floor(min(est_fig_price8 $dif_s, na.rm = TRUE) / 5) * 5,
                 ceiling(max(est_fig_price8 $dif_s, na.rm = TRUE) / 5) * 5,
                 by = 5)  # Set breaks every 5 units
  ) +
  ylim(-100, 0) +  # Set y-axis limits
  labs(
    x = "SQSR - EOSR (K/ac)",
    y = "Estimated Profit Difference($/ac)"
  ) +
  theme(
    legend.position = "right",
    legend.direction = "vertical",# Place the legend at the bottom
     axis.title.x =  element_text(size = 16),
    axis.text = element_text(size = 16),  # Increase axis text size
 axis.title.y = element_text(size = 16),  # Increase x-axis title size
    legend.title = element_text(size = 16),  # Increase legend title font size
    legend.text = element_text(size = 16)    # Increase legend text font size
  )



caption_price3 <- ggplot() + 
  annotate("text", x = 0.5, y = 0.5, label = "At the Hihgest Seed cost over the Recent 10 Years ", 
           size = 8, hjust = 0.5, vjust = 0.5) + 
  theme_void()

caption_price8 <- ggplot() + 
  annotate("text", x = 0.5, y = 0.5, label = "At the Lowest Seed cost over the Recent 10 Years", 
           size = 8, hjust = 0.5, vjust = 0.5) + 
  theme_void()

# Arrange the plots in a 3x2 grid with captions below each type of plot
dif_pro_seed_type_price_3_8 <- (
 dif_pro_seed_type_price3 / caption_price3 / 
  dif_pro_seed_type_price8 / caption_price8
) + plot_layout(ncol = 1, heights = c(6, 1, 6, 1))

# Display the combined plot
print(dif_pro_seed_type_price_3_8)

ggsave(here("Figure","dif_pro_seed_type_price_3_8.png"), plot = dif_pro_seed_type_price_3_8 , width = 14, height = 12, units = "in")


```

##############################################
##############################################
Same Farm multi-year trial result comparison  
###############################################
###############################################

# How difference the yield S response by fields
# How difference the yield S response by year 
# What about EOSR and SQSR and their profits?


```{r Same Farm multi year trial result comparison   , cache = T, results = "hide"}
## "CLC","Bohnhoff","Nelson","Hord","Gingerich","Gould"

## Nelson, 2017,2018,2020,2022,2023
## Hord 2018,2021,2022
## Gingerich 2017,2018,2019,2022,2023
## Gould 2019,2020,2022,2023


create_farm_plot <- function(data) {
  # Unnest and prepare data for plotting
  data_processed <- data %>%
    unnest(eval_s)
  
  # Extract unique `opt_s` and corresponding `yield_hat` values
  unique_points <- data_processed %>%
    group_by(ffy) %>%
    filter(input_rate == unique(opt_s)) %>%
    summarize(opt_s = unique(opt_s), yield_hat = unique(yield_hat), .groups = 'drop')
  
  # Create the plot
  ggplot(data_processed, aes(x = input_rate, y = yield_hat, color = factor(farm_id))) +
    geom_smooth(method = "loess", aes(fill = factor(ffy), color = factor(farm_id)), alpha = 0.3) +
    geom_point(data = unique_points, aes(x = opt_s, y = yield_hat), color = 'red') +
    scale_color_viridis_d(name = "Farm ID") +  # Use Viridis discrete color scale
    labs(
      x = "Seeding Rate (K/ac)",
      y = "Estimated Yield (bu/ac)"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",  # Show legend on the right
      legend.title = element_text(size = 12, face = "bold"),  # Customize legend title
      legend.text = element_text(size = 10),  # Customize legend text
      strip.text = element_text(size = 12),  # Customize facet labels
      strip.background = element_rect(fill = "lightgrey")  # Background color for facet labels
    )
}


# Assuming est_farm contains all the necessary data including farm_id
type_a_1_plot <- create_farm_plot(est_type_a_1)

# Save the plot
ggsave(here("Figure","by_farm_resps_plot.png"), plot = farm_resp_plot, width = 8, height = 4, units = "in", dpi = 300)


```



########################################
UNUSED FIGURES AND TABLES 
############################################

```{r unused figure table , cache = F, results = "hide"}


####################################################################
##### Table2 ( average by ten fields sort by SQSR-EOSR) ############
####################################################################

est_tab2 <- est_bind %>%
  mutate(
    dif_s = stq_s - opt_s,
    dif_y = stq_y - opt_y ,
    dif_p =  stq_p - opt_p 
  ) %>%
  arrange(desc(dif_s))

# Calculate the range and break points for 10 groups
breaks_dif_s <- quantile(est_tab2$dif_s, probs = seq(0, 1, length.out = 11), na.rm = TRUE)

# Assign dif_s_range based on these breaks
est_tab2$dif_s_rank = cut(est_tab2$dif_s, breaks = breaks_dif_s, include.lowest = TRUE, labels = FALSE)


# 3. Generate labels for each range
range_labels <- paste0("(", head(round(breaks_dif_s,2), -1), ", ", tail(round(breaks_dif_s,2), -1), "]")

# 4. Create the dif_s_range variable with these labels
est_tab2$dif_s_range <- range_labels[est_tab2$dif_s_rank]

# Optional: Check the result
head(est_tab2)

### Average net benefit of switching from SQSR to EOSR
mean(est_tab2$opt_s)
mean(est_tab2$stq_s)

mean(abs(est_tab2$dif_p))


mean(abs(est_tab2$dif_s))

### stq_s > opt_s
          
os_field <-  length((which(est_tab2$dif_s> 0)))
os_prof <-round(abs(mean(est_tab2$dif_p[(which(est_tab2$dif_s> 0))])),1)
os_stq_s <- round(mean(est_tab2$stq_s[(which(est_tab2$dif_s> 0))]),1)
os_opt_s <- round(mean(est_tab2$opt_s[(which(est_tab2$dif_s> 0))]),1)

### stq_s < opt_s

us_field <-  length((which(est_tab2$dif_s < 0)))
us_prof <-round(abs(mean(est_tab2$dif_p[(which(est_tab2$dif_s < 0))])),1)
us_stq_s <- round(mean(est_tab2$stq_s[(which(est_tab2$dif_s < 0))]),1)
us_opt_s <- round(mean(est_tab2$opt_s[(which(est_tab2$dif_s < 0))]),1)





### I want to make summary table by using kable
### the table need to be made under the group_by(dif_rank) 
### each column need to show the mean and standard deviation of variable
### the columns will be  dif_s,  dif_y, dif_p, opt_s, opt_y_s, opt_p_s.
### also, the name of the column should be renamed as
### "Seeding Rate(K/ac)",'Estimated Yield(bu/ac)", "Estimated Profit($/ac)", ""Seeding Rate(K/ac)",'Estimated Yield(bu/ac)", "Estimated Profit($/ac)".
### Ane this table requires two header for column(1:3) and column(4:6)
### the header will be "Difference by SQSR and EOSR" and " EOSR"

library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)

# Calculate summary statistics
summary_tab2 <- est_tab2 %>%
  group_by(year,state) %>% 
   arrange(year) %>%
  summarize(
    field_number = n(),
    mean_dif_s = mean(dif_s, na.rm = TRUE),
    sd_dif_s = sd(dif_s, na.rm = TRUE),
    mean_dif_y = mean(dif_y, na.rm = TRUE),
    sd_dif_y = sd(dif_y, na.rm = TRUE),
    mean_dif_p = mean(dif_p, na.rm = TRUE),
    sd_dif_p = sd(dif_p, na.rm = TRUE),
    mean_opt_s = mean(opt_s, na.rm = TRUE),
    sd_opt_s = sd(opt_s, na.rm = TRUE),
    mean_opt_y = mean(opt_y, na.rm = TRUE),
    sd_opt_y = sd(opt_y, na.rm = TRUE),
    mean_opt_p = mean(opt_p, na.rm = TRUE),
    sd_opt_p = sd(opt_p, na.rm = TRUE)
  )

# Combine means and standard deviations into a single format

result_tab2 <- summary_tab2 %>%
  mutate(
      `Field Count` = field_number,
     `Seeding Rate(K/ac)` = paste0(round(mean_opt_s, 2), "<br> (", round(sd_opt_s, 2), ")"),
    `Estimated Yield(bu/ac)` = paste0(round(mean_opt_y, 2), " <br>(", round(sd_opt_y, 2), ")"),
    `Estimated Profit($/ac)` = paste0(round(mean_opt_p, 2), " <br>(", round(sd_opt_p, 2), ")"),
    `Seeding Rate(K/ac) - EOSR` = paste0(round(mean_dif_s, 2), "<br> (", round(sd_dif_s, 2), ")"),
    `Estimated Yield(bu/ac) - EOSR` = paste0(round(mean_dif_y, 2), "<br> (", round(sd_dif_y, 2), ")"),
    `Estimated Profit($/ac) - EOSR` = paste0(round(mean_dif_p, 2), "<br> (", round(sd_dif_p, 2), ")")
  ) %>%
  dplyr::select(year,state,  `Field Count`,`Seeding Rate(K/ac)`, `Estimated Yield(bu/ac)`, `Estimated Profit($/ac)`,`Seeding Rate(K/ac) - EOSR`, `Estimated Yield(bu/ac) - EOSR`, `Estimated Profit($/ac) - EOSR`)


# Create and format the table with kable

res_tab2 <- result_tab2 %>%
  kable("html", escape = FALSE, col.names = c(
    
    "Yeaer","State","Field <br>Counts",
    "Seeding Rate (K/ac)", "Estimated Yield (bu/ac)", "Estimated Profit ($/ac)",
    "Seeding Rate (K/ac)", "Estimated Yield (bu/ac)", "Estimated Profit ($/ac)"
  )) %>%
 kable_styling(
    position = "center",
    # Additional CSS for header alignment
    latex_options = "hold_position",
    full_width = FALSE,
    html_font = "Arial",
    bootstrap_options = c("striped", "hover", "condensed"),
    font_size = 10
  ) %>%
     add_header_above(c("-"=3,"EOSR" = 3," Differences between SQSR and EOSR" =3 ), align = "c") %>%
  row_spec(0, bold = TRUE, extra_css = "text-align: center;") %>%
  column_spec(1:ncol(data_tab2), extra_css = "text-align: center;") 



####


writeLines(res_tab2
, "result_tab2.html")

library(webshot2)

# Convert HTML to PNG
webshot("result_tab2.html", file = "result_tab2.png", vwidth = 600, vheight = 700)



###########################################
#### SQSR , EOSR COMPARISON TABLE #####
###########################################
est_stq <- est_bind %>%
  arrange(stq_s) %>%                    # Arrange by 'stq_s'
  mutate(row_number = 1:nrow(.))        # Update row_number based on the new order

 
library(RColorBrewer)

# Define grayscale colors for each range
gray_colors <- c("22~24" = "#D3D3D3",    # Light gray
                  "28~30" = "#A9A9A9",    # Darker gray
                  "32~33.5" = "#808080",   # Medium gray
                  "34~35.5" = "#595959",   # Even darker gray
                  "36~38" = "#333333")     # Darkest gray


green_colors <- c("22~24" = "#D0F0C0",    # Pale green
                   "28~30" = "#9ACD32",    # Yellow-green
                   "32~33.5" = "#6B8E23",   # Olive drab
                   "34~35.5" = "#3C6B5E",   # Darker green
                   "36~38" = "#004d00")     # Very dark green

# Define the ranges for the grayscale colors
range_breaks <- c(21, 24, 30, 33.5, 35.5, 38)

# Create a new factor variable that maps each stq_s to its corresponding range

est_stq$stq_s_range <- cut(
  est_stq$stq_s,
  breaks = range_breaks,
  labels = names(green_colors),
  right = TRUE
)

# Ensure the color mapping is based on the levels of the factor variable
color_mapping <- green_colors[levels(est_stq$stq_s_range)]

# Create the plot
opt_stq_by_stq <- ggplot(est_stq, aes(x = row_number, y = diff_s, fill =stq_s_range)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = state), y = 0, hjust = 0.5, size = 2, color = "black") +  # Place text at y = 0
  labs(x = "Status Quo Seeding Rate", y = "Optimal - Status Quo Seeding Rate", title = "Difference Between Optimal and Status Quo Seeding Rate", fill = "Status Quo Seeding Rate Range") +
  scale_fill_manual(values = color_mapping) +  # Use grayscale colors
  theme_minimal() +
  scale_x_continuous(
    breaks = NULL,  # Remove breaks
    labels = NULL   # Remove labels
  ) +
  theme(
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank()  # Remove x-axis ticks
  )

# Print the plot
print(opt_stq_by_stq)


##########################
ggsave("opt_stq_by_stq.pdf", plot = opt_stq_by_stq, width = 16, height = 6)
###########################


# Create a new factor variable that maps each stq_s to its corresponding range

# Sort the data by year and stq_s
est_year <- est_stq %>%
  arrange(year, stq_s) %>% 
   mutate(row_number = 1:nrow(.)) 

est_year <- est_stq %>%
  arrange(year, stq_s) %>% 
  group_by(year) %>% 
  mutate(row_number = row_number()) %>% 
  ungroup()


# Calculate the range for y-axis
y_limits <- range(est_year$diff_s, na.rm = TRUE)

# Ensure the color mapping is based on the levels of the factor variable
color_mapping <- green_colors[levels(est_year$stq_s_range)]

# Create the faceted plot
opt_stq_by_year <- ggplot(est_year, aes(x = row_number, y = diff_s, fill = stq_s_range)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = state), y = 0, hjust = 0.5, size = 2, color = "black") +  # Place text at y = 0
  labs(x = "Status Quo Seeding Rate", y = "Optimal - Status Quo Seeding Rate", title = "Difference Between Optimal and Status Quo Seeding Rate", fill = "Status Quo Seeding Rate Range") +
  scale_fill_manual(values = color_mapping) +  # Use grayscale colors
  theme_minimal() +
  scale_x_continuous(
    breaks = NULL,  # Remove breaks
    labels = NULL   # Remove labels
  ) +
  scale_y_continuous(
    limits = y_limits,  # Set the y-axis limits
    breaks = seq(floor(y_limits[1]), ceiling(y_limits[2]), by = (ceiling(y_limits[2]) - floor(y_limits[1])) / 5)  # Adjust breaks based on range
  ) +
  theme(
    axis.text.x = element_blank(),  # Remove x-axis text
    axis.ticks.x = element_blank()  # Remove x-axis ticks
  ) +
  facet_wrap(~ year, scales = "fixed")  # Fixed scales for consistent y-axis

# Print the faceted plot
print(opt_stq_by_year)


##########################
ggsave("opt_stq_by_year.pdf", plot = opt_stq_by_year, width = 16, height = 12)
###########################
 

################
##### By Farm
#####################

### First check how many trials by farm #####


farm_counts <- est_bind %>%
  group_by(farm) %>%       # Group by 'farm'
  summarize(count = n())  %>%# Count the number of rows in each group
   filter(count >2)

print(farm_counts,n=11)




 est_bind_part <- est_bind %>%
  arrange(diff_s) %>%
   filter(diff_s < quantile(diff_s, 0.25) | diff_s > quantile(diff_s, 0.75))
  

 ########################################################
###### Yield respone , opt_s, stq_s, usda_s. ###########
########################################################


plots_yield_seed <- list()



for (i in 1:nrow(est_bind_part)) {
  # Extract data for the current row
  comb_i <- est_bind_part[i,]
  eval_i <-est_bind_part[i,]$eval[[1]]
  dat_i <-est_bind_part[i,]$anal[[1]]
  opt_s_y_i <- est_bind_part[i,]$opt_s_y_ffy[[1]]
 
   # Add ff_id to eval_data
  eval_i$ff_id <-comb_i$ff_id
  
  # Create a scatter plot of yield response to seed
  plot <- ggplot(eval_i, aes(x=input_rate,y=yield_hat)) +
  #  geom_point(data=dat_i,aes(x=s_rate,y=yield))+
    geom_smooth(method = "gam", se = TRUE, size = 0.5, color = 'brown',lwd=1,
                alpha=0.5)+
    geom_point(dat=dat_i,aes(x=s_rate,y=yield),alpha=0.5, size=0.1) +
    geom_point(dat=opt_s_y_i, aes(x=opt_s_ffy,y=opt_y_ffy),color = "blue",size=0.25)+
  
   # labs(title = paste(il_dk_sel$ff_id[i])) +  # Add experiment title
    xlab("Seed") + ylab("Yield") +
    xlim(15, 40) + ylim(100, 275) +
      
    geom_hline(yintercept = comb_i$stq_y, color = "red", lty = 'dashed', lwd = 0.5) +
      geom_point(x= comb_i$stq_s, y = comb_i$stq_y, color = "red",size=0.5) +

        geom_hline(yintercept = comb_i$opt_y, color = "blue", lty = 'dashed', lwd = 0.5) +
      geom_point(x= comb_i$opt_s, y = comb_i$opt_y, color = "blue",size=0.5) +

    
     geom_hline(yintercept = comb_i$usda_y, color = "green", lty = 'dashed', lwd = 0.5,alpha=0.5) +
      geom_point(x= comb_i$usda_s, y = comb_i$usda_y, color = "green",size=0.5) +
    # Add vertical line for status quo
    theme(
      axis.title = element_text(size = 6),  # Adjust axis title font size
      axis.text = element_text(size = 6),   # Adjust axis text font size
      plot.title = element_text(size = 8),  # Adjust plot title font size
      panel.spacing = unit(0, "lines")      # Remove space between facets
    ) +
    facet_wrap(~ ff_id, ncol = 6, scales = "free")  # Use facet_wrap to arrange plots
    
  # Add the plot to the list
  plots_yield_seed[[i]] <- plot
}


 


opt_stq_state_year <-ggplot(est_year, aes(x = row_number, y = diff_s, fill = factor(year))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = state), vjust = -0.5,size=2) +
  labs(x = "Field", y = "Optimal Seeding - Status quo Seeding", title = "Difference between optimal seeding and status quo seeding by state and year", fill = "Year") +
  scale_fill_brewer(palette = "Set1") +  # Use a color palette
  theme_minimal()

ggsave("opt_stq_seeding_state_year.pdf", plot = opt_stq_state_year, width = 8, height = 6)


custom_colors <- viridis(25)
est_farm <- est_bind %>% arrange(year)
est_farm$row_number <- 1:nrow(est_farm)


opt_stq_farm_year <-ggplot(est_farm, aes(x = row_number, y = diff_s, fill = factor(farm_id))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = farm_id), vjust = -0.5,size=2) +
  labs(x = "Field", y = "Optimal Seeding - Status quo Seeding", title = "Difference between optimal seeding and status quo seeding by farm and year", fill = "farm_id") +
scale_fill_viridis(discrete = TRUE, option = "D") +  # Use a color palette
   theme_minimal()

hist(est_farm$stq_s)

ggsave("opt_stq_seeding_farm_year.pdf", plot = opt_stq_farm_year, width = 8, height = 6)




 
 
 
 ### First
### Look at the IL by year

est_bind_il <- est_bind %>% filter(state == 'IL') %>%
  arrange(year)







#### Check est_bind_part by 




# Loop through each row

est_bind_il





est_bind_part <- est_bind %>%
  arrange(diff_s) %>%
   filter(diff_s < quantile(diff_s, 0.25) | diff_s > quantile(diff_s, 0.75))
  
########################################################
###### Yield respone , opt_s, stq_s, usda_s. ###########
########################################################


plots_yield_seed <- list()



for (i in 1:nrow(est_bind_part)) {
  # Extract data for the current row
  comb_i <- est_bind_part[i,]
  eval_i <-est_bind_part[i,]$eval[[1]]
  dat_i <-est_bind_part[i,]$anal[[1]]
  opt_s_y_i <- est_bind_part[i,]$opt_s_y_ffy[[1]]
 
   # Add ff_id to eval_data
  eval_i$ff_id <-comb_i$ff_id
  
  # Create a scatter plot of yield response to seed
  plot <- ggplot(eval_i, aes(x=input_rate,y=yield_hat)) +
  #  geom_point(data=dat_i,aes(x=s_rate,y=yield))+
    geom_smooth(method = "gam", se = TRUE, size = 0.5, color = 'brown',lwd=1,
                alpha=0.5)+
    geom_point(dat=dat_i,aes(x=s_rate,y=yield),alpha=0.5, size=0.1) +
    geom_point(dat=opt_s_y_i, aes(x=opt_s_ffy,y=opt_y_ffy),color = "blue",size=0.25)+
  
   # labs(title = paste(il_dk_sel$ff_id[i])) +  # Add experiment title
    xlab("Seed") + ylab("Yield") +
    xlim(15, 40) + ylim(100, 275) +
      
    geom_hline(yintercept = comb_i$stq_y, color = "red", lty = 'dashed', lwd = 0.5) +
      geom_point(x= comb_i$stq_s, y = comb_i$stq_y, color = "red",size=0.5) +

        geom_hline(yintercept = comb_i$opt_y, color = "blue", lty = 'dashed', lwd = 0.5) +
      geom_point(x= comb_i$opt_s, y = comb_i$opt_y, color = "blue",size=0.5) +

    
     geom_hline(yintercept = comb_i$usda_y, color = "green", lty = 'dashed', lwd = 0.5,alpha=0.5) +
      geom_point(x= comb_i$usda_s, y = comb_i$usda_y, color = "green",size=0.5) +
    # Add vertical line for status quo
    theme(
      axis.title = element_text(size = 6),  # Adjust axis title font size
      axis.text = element_text(size = 6),   # Adjust axis text font size
      plot.title = element_text(size = 8),  # Adjust plot title font size
      panel.spacing = unit(0, "lines")      # Remove space between facets
    ) +
    facet_wrap(~ ff_id, ncol = 6, scales = "free")  # Use facet_wrap to arrange plots
    
  # Add the plot to the list
  plots_yield_seed[[i]] <- plot
}


# Save the plots side by side using grid.arrange

# Save the plots side by side using grid.arrange
ggsave(filename = "combined_yield_seed_by_diff_seeding.pdf", plot = grid.arrange(grobs =  plots_yield_seed, ncol = 6), width = 48, height = 48)


######### Now, we need to check 
#####. 1. by state and year (to see how diff opt,stq, usda)
####. 2. by negative and positive ( opt < stq ,  opt > stq )
####. After that look into the characteristics or weather situation 

comb_df <- comb_df %>%
  mutate(ff = str_extract(ff_id, "^[^_]+_[^_]+"))

#opt_s, stq_s, usda_s

### Okay, BARPLOT DOES NOT LOOK GOOD AT ALL
### Let's make table instead 
### table of opt_s,stq_s,usda_s by state and year on the left side
### table of opt_p,stq_p, usda_p by  state and year on the right side 
### (or make separate table for seed and profit)

library(knitr)
library(kableExtra)


comb_df<-readRDS(here("comb_df.RDS"))

# Arrange and round the relevant columns
table_df <- comb_df %>%
  arrange(year, state) %>%
  mutate(opt_s = round(opt_s, 1)) %>%
  dplyr::select(year, state, ff, opt_s, stq_s, usda_s)

# Create a list to store the tables
tables_list <- list()

# Loop through each unique combination of year and state
unique_years <- unique(table_df$year)
unique_states <- unique(table_df$state)

# Generate tables and store them in a list
for (year_i in unique_years) {
  for (state_i in unique_states) {
    subset_df <- table_df %>%
      filter(year == year_i & state == state_i) %>%
      dplyr::select(ff, opt_s, stq_s, usda_s)  # Exclude year and state columns from the subset
    
    table_caption <- paste("Year:", year_i, "State:", state_i)
    
    tables_list[[paste(state_i, year_i, sep = "_")]] <- kable(subset_df, format = "html", caption = table_caption) %>%
      kable_styling("striped", full_width = FALSE)
  }
}

# Create a grid layout for the tables
cat("<div style='display: grid; grid-template-columns: repeat(8, 1fr); gap: 20px;'>")

# Header row for years
cat("<div></div>") # Empty top-left cell
for (year_i in unique_years) {
  cat(paste("<div style='font-weight: bold; text-align: center;'>Year:", year_i, "</div>"))
}

# Rows for states
for (state_i in unique_states) {
  cat(paste("<div style='font-weight: bold; text-align: center;'>State:", state_i, "</div>")) # State label
  for (year_i in unique_years) {
    table_id <- paste(state_i, year_i, sep = "_")
    if (!is.null(tables_list[[table_id]])) {
      cat("<div style='border: 1px solid #ddd; padding: 10px;'>")
      print(tables_list[[table_id]])
      cat("</div>")
    } else {
      cat("<div style='border: 1px solid #ddd; padding: 10px;'>No Data</div>")
    }
  }
}
cat("</div>")




  # Reshape the data
comb_long <- comb_df %>%
  pivot_longer(cols = c(opt_s, stq_s, usda_s), names_to = "variable", values_to = "value")


# Create a ggplot object for horizontal barplot with faceting
p <- ggplot(comb_long, aes(y = ff, x = value, fill = variable)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(year ~ state, scales = "free_y", space = "free_y") +
  theme_minimal() +
  labs(y = "ff", x = "Value", fill = "Variable") +
  theme(axis.text.y = element_text(angle = 0, hjust = 1))

# Print the plot
print(p)



under_seed_prec <- ggplot(combined_us) +
  geom_point(aes(x =status_quo - opt_s,y=prec_in, color = "Under Seed Density"))+
 labs(title = "O",
       y = "Experiment ID",
       x = "Seed Rates",
       fill = "Seed Rates") +
  scale_fill_manual(values = c("blue", "red")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0),
        legend.position = "bottom")

  geom_point(aes(x = status_quo,y=prec_in,color='Status Quo Seed'))

  geom_bar(aes(x = status_quo, fill = "Status Quo"), stat = "identity", position = position_nudge(y = 0.1),width=0.2) +
  labs(title = "Opt Input vs Status Quo",
       y = "Experiment ID",
       x = "Seed Rates",
       fill = "Seed Rates") +
  scale_fill_manual(values = c("blue", "red")) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0),
        legend.position = "bottom")






















###### 2. Estimated profit by opt_s, stq_s, usda_s
###### by state and year












## 50 from IL, OK 10 , SD 12, OH4, MN2, KS1
## 

ggplot(combined_us, aes(x = status_quo)) +
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(title = "Histogram of Status Quo",
       x = "Status Quo",
       y = "Frequency")


# Create the thematic map
tm_shape(us_map) +
  # Specify the fill color or pattern for the polygons using Viridis color scale
  tm_fill(col = "grey" ) +
  
  # Overlay the points on top of the polygons
  tm_shape(combined_us) +
  # Specify the points and their properties
  tm_dots(col = "farm",palette = "viridis") +

  # Customize legend position
  tm_layout(legend.outside = TRUE, legend.position = c("right", "bottom"))

tm_tgts <- tm_shape(trial_s) +
  tm_fill(
    col = "tgts_K", 
    palette = "Greens",
     title = "Seed (Thou/ac)",
    style = "cat",
  
  )


status_quo_prec <- ggplot(combined_us) +
  geom_point(aes(x =  prec_in, y =status_quo, color =state_name)) +
  labs(title = "In Season Average Precipitation and Status_quo Seed Rate ",
       y = "Status Quo Seed rate",
       x = "Precipitation",
  ) +  scale_color_viridis_d(option = "C") +  # Use Viridis color scale
  theme_minimal()

ggsave("status_quo_prec.png", plot = status_quo_prec, width = 5, height = 5, units = "in")




opt_prec <- ggplot(combined_us) +
  geom_point(aes(x = prec_in, y =opt_s , color =state_name)) +
  labs(title = "In Season Average Precipitation and Estimated Optimal Seed Rate ",
       y = "Estimated Opt Seed rate",
       x = "Precipitation",
  ) +  scale_color_viridis_d(option = "C") +  # Use Viridis color scale
  theme_minimal()


ggsave("opt_prec.png", plot = opt_prec, width = 5, height = 5, units = "in")


######### 
##combined_us
##
## 1. Trials by year and state
## 2. Trials by year and location
## 3. 


###### Now take 2022 fields figures 
# 
# plot_list <- list() 
# 
# for (i in include_plots) {
#   # Create the yield-seed response curve
#   s_rate_range <- range(eval_bind[[i]][[1]]$input_rate, na.rm = TRUE)
#   opt_seed <- opt_bind[[i]][[1]]$opt_input
#   
#   status_quo <- status_quo_bind[[i]][[1]]
#   if(status_quo > 1000){
#     status_quo <- status_quo / 1000
#   }  
# # Create the yield-seed curve plot
# yield_seed_curve <- ggplot(data_anal_bind[[i]], aes(x = s_rate, y = yield)) +
#   geom_point() +
#   geom_point(data=eval_bind[[i]][[1]], aes(x=input_rate, y= yield_hat),col='pink',size=0.5) +
#  geom_vline(xintercept = opt_seed, color = "green", linetype = "dashed",
#             lwd=1) +
#  geom_vline(xintercept = status_quo, color = "blue", linetype = "dashed",
#             lwd=1) +
#   geom_smooth(method = "lm", formula = y ~ poly(x, 2), se = FALSE, color='yellow',lwd=0.5) +
#   labs(title = paste(combined_df[i]$exp_id, "Yield-Seed Response"),
#        x = "Seed(k/ac)", y = "Yield(bu/ac)") +
#   xlim(s_rate_range) + # Set x-axis limits
#   annotate("text", x = opt_seed, y = max(data_anal_bind[[i]]$yield), 
#            label = "opt_seed", color = "green", fontface = "italic") +
#    annotate("text", x = status_quo, y = max(data_anal_bind[[i]]$yield), 
#            label = "status_quo", color = "blue", fontface = "italic")
#  
# 
# ggsave(filename = here("save_image_2022",paste0(combined_df[i]$exp_id,"_yield_seed.png")),
#        plot = yield_seed_curve)
# 
# 
# plot_list[[i]] <- yield_seed_curve
# 
# 
# 
# }
# 
# saveRDS(plot_list, here("save_image","plot_list.rds"))






#################################
# 1.pick one field and create a map of seed rate experimental design and yield map
#########################

breaks <- c(50, 75, 100, 125, 150, 175, 200, 225, 250)

tm_tgts <- tm_shape(trial_s) +
  tm_fill(
    col = "tgts_K", 
    palette = "Greens",
     title = "Seed (Thou/ac)",
    style = "cat",
  
  ) +
  tm_layout_to_add + 
  tm_layout(
     legend.text.size = 0.8,
              legend.title.size=1
)


tm_yield <- tm_shape(yield) +
  tm_dots(
    col = "Yld_Vol_Dr", 
    palette = "YlOrBr",
    title = "Yield (bu/ac)",
    style = "cont",  # Change style to continuous
    breaks = breaks
  ) +
  tm_layout_to_add + 
  tm_layout(
    legend.outside.position = "right",
    legend.position = c(0.01, 0.25),
    legend.text.size = 0.8,
    legend.title.size = 1
  ) 

###################################
# 2.the yield response figure for the six fields with consistent y-axis and x-axis
#######################################


# Initialize list to store plots
plots_yield_seed <- list()

# Loop through each row of il_dk_sel
for (i in 1:nrow(combined_df)) {
  # Extract data for the current row
  eval_data <-combined_df$eval_data[[i]]
  
   # Add ff_id to eval_data
  eval_data$ff_id <-combined_df$ff_id[i]
  
  # Create a scatter plot of yield response to seed
  plot <- ggplot(eval_data, aes(x = input_rate, y = yield_hat)) +
    geom_smooth(method = "gam", se = TRUE, size = 0.5, color = 'black') +
   # labs(title = paste(il_dk_sel$ff_id[i])) +  # Add experiment title
    xlab("Seed") + ylab("Yield") +
    xlim(15, 40) + ylim(100, 275) +
    geom_vline(xintercept = combined_df$status_quo[i], color = "red", lty = 'dashed', lwd = 0.5) +  # Add vertical line for status quo
    geom_vline(xintercept = combined_df$opt_input[i], color = "blue", lty = 'dashed', lwd = 0.5) +   # Add vertical line for optimal input
    theme(
      axis.title = element_text(size = 6),  # Adjust axis title font size
      axis.text = element_text(size = 6),   # Adjust axis text font size
      plot.title = element_text(size = 8),  # Adjust plot title font size
      panel.spacing = unit(0, "lines")      # Remove space between facets
    ) +
    facet_wrap(~ ff_id, ncol = 6, scales = "free")  # Use facet_wrap to arrange plots
    
  # Add the plot to the list
  plots_yield_seed[[i]] <- plot
}

# Save the plots side by side using grid.arrange

# Save the plots side by side using grid.arrange
ggsave(filename = "combined_yield_seed.pdf", plot = grid.arrange(grobs =  plots_yield_seed, ncol = 6), width = 12, height = 20)


#######################################
# 3. table of profit loss of using the farmer-chosen rate relative to EOSR for all the fields
##############################

combined_df$opt_profit<- 1
combined_df$sq_profit<- 1

for(i in 1:length(combined_df$exp_id)){
  
   opt_row<- which.min(abs(combined_df$eval_data[[i]]$input_rate -combined_df[i,]$opt_input))
   
  sq_row<- which.min(abs(combined_df$eval_data[[i]]$input_rate -combined_df[i,]$status_quo))
  
combined_df$opt_profit[i] <-  combined_df$eval_data[[i]]$profit_hat[opt_row]

combined_df$sq_profit[i] <-  combined_df$eval_data[[i]]$profit_hat[sq_row]
}

# Calculate the differences between opt_profit and sq_profit by ff_id
combined_df <- combined_df %>%mutate(prof_dif = opt_profit - sq_profit)


# Determine the range for breaks
min_prof_dif <- floor(min(combined_df$prof_dif))
max_prof_dif <- ceiling(max(combined_df$prof_dif))

# Create bar plot with adjusted bar size and spacing
bar_plot <- ggplot(combined_df, aes(x = prof_dif, y = ff_id)) +
  geom_bar(stat = "identity", fill = "red", color = "black", size = 0.4, width = 0.5) +  # Adjust width here
  scale_y_discrete(expand = expansion(add = c(0.05, 0.05))) +  # Adjust vertical spacing between bars
  scale_x_continuous(breaks = seq(min_prof_dif, max_prof_dif, by = 10)) +  # Adjust x-axis breaks
  labs(title = "Net Revenue loss by applying farmer's status quo",
       x = "Revenue Loss ($/ac)",
       y = "Field ID") +
  theme_minimal()

# Save horizontal bar plot to PDF
ggsave("prof_dif_barplot.pdf", plot = bar_plot,width = 8, height = 15, units = "in")


```



